---
title: "2020 German IT Salaries"
author: "Dylan Montenegro"
date: "5/3/2022"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Introduction

- Who gets paid the most?
- What skills and how much experience do you need in order to have a higher salary?

## Tools Required

```{r, echo = TRUE}
library(knitr) # used for dynamic report generation
library(rmarkdown) # document conversion
library(ggplot2) #used for data visualization
library(plotly) #used for interactive plots
library(dplyr) #used for data manipulation
library(readr) #used to read rectangular data
```

## Data Source

- [IT Salary Survey for EU Region(2018-2020)] (https://www.kaggle.com/datasets/parulpandey/2020-it-salary-survey-for-eu-region?resource=download)
- Survey made by Sergey Vasilyev.
- Survey is done once a year.

## Data Import and Preparation

```{r, echo=TRUE}
Salaries <- read_csv('~/Desktop/Data2401/archive/IT Salary Survey EU  2020.csv')
```
### Preparation
```{r, echo=TRUE}
Salaries <- Salaries %>% mutate(Base_Salary = `Yearly brutto salary (without bonus and stocks) in EUR`)

Salaries <- Salaries %>% select(- c(Timestamp, `Years of experience in Germany`, `Yearly brutto salary (without bonus and stocks) in EUR`, `Yearly bonus + stocks in EUR`, `Other technologies/programming languages you use often`, `Annual brutto salary (without bonus and stocks) one year ago. Only answer if staying in the same country`, `Annual bonus+stocks one year ago. Only answer if staying in same country`, `Have you lost your job due to the coronavirus outbreak?`, `Have you been forced to have a shorter working week (Kurzarbeit)? If yes, how many hours per week`, `Have you received additional monetary support from your employer due to Work From Home? If yes, how much in 2020 in EUR`, `Employment status`, `Number of vacation days`))

Salaries <- Salaries %>% group_by(City) %>% mutate(number_responses_per_city = n())
Salaries <- Salaries %>% group_by(Position) %>% mutate(number_people_per_position = n())
Salaries <- Salaries %>% group_by(`Your main technology / programming language`) %>% mutate(number_people_per_main_tech= n())


x <- Salaries$`Your main technology / programming language`
Salaries$`Your main technology / programming language` <- toupper(x)


my_swap <- function(old, new1){ 
    test <- Salaries      
  test$`Your main technology / programming language`[test$`Your main technology / programming language` == old] <- new1
  return(test)
}


my_swap2 <- function(old2, new2){ 
    test2 <- Salaries  
    test2$`Total years of experience`[test2$`Total years of experience` == old2]  <- new2
  return(test2)
}


my_swap4 <- function(old4, new4){
  test4 <- Salaries
  test4$`Company type`[test4$`Company type` == old4] <- new4
  return(test4)
}

my_swap5 <- function(old5, new5){
  test5 <- Salaries
  test5$`City`[test5$`City` == old5] <- new5
  return(test5)
}

my_swap6 <- function(old6, new6){
  test6 <- Salaries
  test6$`Main language at work`[test6$`Main language at work` == old6] <- new6
  return(test6)
}

my_swap7 <- function(old7, new7){
  test7 <- Salaries
  test7$`Seniority level`[test7$`Seniority level` == old7] <- new7
  return(test7)
}

my_swap8 <- function(old8, new8){
  test8 <- Salaries
  test8$`Position`[test8$`Position` == old8] <- new8
  return(test8)
}
```

```{r, echo=FALSE}
Salaries <- my_swap('SAS,SQL,PYTHON', 'SAS')
Salaries <- my_swap('ОФМФ', "JAVA")
Salaries <- my_swap('.NET, ANGULAR', '.NET')
Salaries <- my_swap('.NET, C++, SPSS, EMBEDDDED', '.NET')
Salaries <- my_swap('ANDROID/KOTLIN', 'ANDROID')
Salaries <- my_swap('ANGULAR, REACT','ANGULAR')
Salaries <- my_swap('ANGULAR, TYPESCRIPT','ANGULAR')
Salaries <- my_swap('ATLASSIAN JIRA','JIRA')
Salaries <- my_swap('AWS HADOOP POSTGRE TYPESCRIPT','AWS')
Salaries <- my_swap('AWS, GCP, PYTHON,K8S','AWS')
Salaries <- my_swap('AZURE, SAP','AZURE')
Salaries <- my_swap('BI, DWH, ETL/ELT','SAP')
Salaries <- my_swap('C, C++','C')
Salaries <- my_swap('C, MATLAB','C')
Salaries <- my_swap('C/C++','C')
Salaries <- my_swap('C#','C')
Salaries <- my_swap('C# .NET','C')
Salaries <- my_swap('C#, .NET CORE','C')
Salaries <- my_swap('C#/.NET','C')
Salaries <- my_swap('C++','C')
Salaries <- my_swap('C++, C#','C')
Salaries <- my_swap('C++, JAVA, EMBEDDED C','C')
Salaries <- my_swap('C++/C','C')
Salaries <- my_swap('C++/C#','C')
Salaries <- my_swap('DJANGO, FLASK, PLOTLY DASH','DJANGO')
Salaries <- my_swap('EMBEDDED C++','C')
Salaries <- my_swap('FRONTEND: REACT, NODE.JS','REACTJS')
Salaries <- my_swap('FRONTEND','REACTJS')
Salaries <- my_swap('GO, PHP, SQL','GO')
Salaries <- my_swap('GO/PYTHON','GO')
Salaries <- my_swap('GOLANG','GO')
Salaries <- my_swap('GRAILS, GROOVY','JAVA')
Salaries <- my_swap('JAVA / SCALA','JAVA')
Salaries <- my_swap('JAVA & DISTRIBUTED SYSTEMS STUFF','JAVA')
Salaries <- my_swap('JAVA & PHP','JAVA')
Salaries <- my_swap('JAVA BACKEND','JAVA')
Salaries <- my_swap('JAVA, .NET','JAVA')
Salaries <- my_swap('JAVA, ANGULAR, AWS','JAVA')
Salaries <- my_swap('JAVA, JAVASCRIPT','JAVA')
Salaries <- my_swap('JAVA, JS','JAVA')
Salaries <- my_swap('JAVA, KOTLIN','JAVA')
Salaries <- my_swap('JAVA, TERRAFORM','JAVA')
Salaries <- my_swap('JAVA/C++','JAVA')
Salaries <- my_swap('JAVA/GROOVY','JAVA')
Salaries <- my_swap('JAVA/KOTLIN','JAVA')
Salaries <- my_swap('JAVA/SCALA','JAVA')
Salaries <- my_swap('JAVA/SCALA/GO/CLOUDS/DEVOPS','JAVA')
Salaries <- my_swap('JAVASCRIPT / TYPESCRIPT','JAVASCRIPT')
Salaries <- my_swap('JAVASCRIPT, TYPESCRIPT','JAVASCRIPT')
Salaries <- my_swap('JAVASCRIPT, ANGULAR','JAVASCRIPT')
Salaries <- my_swap('JAVASCRIPT/ES6','JAVASCRIPT')
Salaries <- my_swap('JAVSCRIPT','JAVASCRIPT')
Salaries <- my_swap('JAVASCRIPT/TYPESCRIPT','JAVASCRIPT')
Salaries <- my_swap('JS, JAVA','JAVASCRIPT')
Salaries <- my_swap('KOTLIN, JAVA','KOTLIN')
Salaries <- my_swap('PYTHON / JAVASCRIPT (REACT)','PYTHON')
Salaries <- my_swap('REACT / JAVASCRIPT','REACTJS')
Salaries <- my_swap('TYPESCRIPT, JAVASCRIPT','TYPESCRIPT')
Salaries <- my_swap('JENKINS BASH','JAVA')
Salaries <- my_swap('JS','JAVASCRIPT')
Salaries <- my_swap('JS, JAVA','JAVASCRIPT')
Salaries <- my_swap('JS, REACTJS','JAVASCRIPT')
Salaries <- my_swap('JS, TYPESCRIPT, ANGULAR','JAVASCRIPT')
Salaries <- my_swap('JS, WDIO','JAVASCRIPT')
Salaries <- my_swap('KOTLIN, JAVA','KOTLIN')
Salaries <- my_swap('KOTLIN/PHP','KOTLIN')
Salaries <- my_swap('KUBERENETES, OPENSTACK','KUBERNETES')
Salaries <- my_swap('KUBERNETES, TERRAFORM, GCP','KUBERNETES')
Salaries <- my_swap('KUBRRNETES','KUBERNETES')
Salaries <- my_swap('LINUX KERNEL','LINUX')
Salaries <- my_swap('LINUX/UNIX, GIT, VIRTUALISATION PLATFORMS, *SHELL(S) SCRIPTS','LINUX')
Salaries <- my_swap('ML/PYTHON','ML')
Salaries <- my_swap('NLP, PYTHON','PYTHON')
Salaries <- my_swap('NODE','NODEJS')
Salaries <- my_swap('NODEJS, TYPESCRIPT, AWS','NODEJS')
Salaries <- my_swap('NODEJS/TS','NODEJS')
Salaries <- my_swap('NODSJS','NODEJS')
Salaries <- my_swap('NODE.JS', 'NODEJS')
Salaries <- my_swap('OBJECTIVE-C ','C')
Salaries <- my_swap('PASCAL, VB.NET, C#','PASCAL')
Salaries <- my_swap('PHP, JS, PYTHON, DOCKER','PHP')
Salaries <- my_swap('PHP/MYSQL','PHP')
Salaries <- my_swap('PL/SQL','PL')
Salaries <- my_swap('PS, SKETCH, REACT, CSS3','PS')
Salaries <- my_swap('PYRHON','PYTHON')
Salaries <- my_swap('PYTHIN','PYTHON')
Salaries <- my_swap('PYTHON (DJANGO)','PYTHON')
Salaries <- my_swap('PYTHON + SQL','PYTHON')
Salaries <- my_swap('PYTHON, CLOUD COMPUTING','PYTHON')
Salaries <- my_swap('PYTHON, DATABASE TECHNOLOGIES','PYTHON')
Salaries <- my_swap('PYTHON, PYTORCH','PYTHON')
Salaries <- my_swap('PYTHON, SCALA','PYTHON')
Salaries <- my_swap('PYTHON, SQL','PYTHON')
Salaries <- my_swap('PYTHON, STATISTICS, SQL','PYTHON')
Salaries <- my_swap('PYTHON, WHOLE APACHE DATA SCIENCE STACK, AWS','PYTHON')
Salaries <- my_swap('PYTHON/NLP','PYTHON')
Salaries <- my_swap('PYTHON/SQL','PYTHON')
Salaries <- my_swap('QLIK BI TOOL, SQL','QLIK')
Salaries <- my_swap('REACT / JAVASCRIPT','REACTJS')
Salaries <- my_swap('REACT JS','REACTJS')
Salaries <- my_swap('REACT.JS / TYPESCRIPT','REACTJS')
Salaries <- my_swap('REACT/TYPESCRIPT','REACTJS')
Salaries <- my_swap('SAP / ABAP','ABAP')
Salaries <- my_swap('SAP ABAP','ABAP')
Salaries <- my_swap('SAP BW / ABAP','ABAP')
Salaries <- my_swap('SCALA / PYTHON','SCALA')
Salaries <- my_swap('SCALA, APACHE SPARK','SCALA')
Salaries <- my_swap('SCALA, REACT.JS','SCALA')
Salaries <- my_swap('SKETCH, FIGMA','SKETCH')
Salaries <- my_swap('SPARK, PYTORCH','SPARK')
Salaries <- my_swap('SQL, BQ, TABLEAU, GTM, GA','SQL')
Salaries <- my_swap('SWIFT, OBJECTIVE-C','SWIFT')
Salaries <- my_swap('SWIFT, OBJECTIVE-C, IOS','SWIFT')
Salaries <- my_swap('SWIFT/KOTLIN','SWIFT')
Salaries <- my_swap('TERRAFORM, KUBERNETES, AWS, GCP, ANSIBLE, PUPPET','TERRAFORM')
Salaries <- my_swap('TS','TYPESCRIPT')
Salaries <- my_swap('TYPESCRIPT / ANGULAR','TYPESCRIPT')
Salaries <- my_swap('TYPESCRIPT, JAVASCRIPT','TYPESCRIPT')
Salaries <- my_swap('TYPESCRIPT, KOTLIN','TYPESCRIPT')
Salaries <- my_swap('TYPESCRIPT, REACT','TYPESCRIPT')
Salaries <- my_swap('TYPESCRIPT, WEB APPS','TYPESCRIPT')
Salaries <- my_swap('TYPESCRIPT/ANGULAR','TYPESCRIPT')
Salaries <- my_swap('Java', 'JAVA')
Salaries <- my_swap('GOOGLE CLOUD PLATFORM', 'GCP')
Salaries <- my_swap('OBJECTIVE-C', 'C')
Salaries <- my_swap('APACHE SPARK', 'SPARK')
Salaries <- my_swap('REACT', 'REACTJS') 
Salaries <- my_swap('RUBY ON RAILS', 'RUBY')
Salaries <- my_swap('T-SQL', 'SQL')

Salaries <- my_swap2('1 (as QA Engineer) / 11 in total', '1')
Salaries <- my_swap2('15, thereof 8 as CTO', '15')
Salaries <- my_swap2('2,5', '2.5')
Salaries <- my_swap2('383', '38')
Salaries <- my_swap2('6 (not as a data scientist, but as a lab scientist)', '0')
Salaries <- my_swap2('less than year', '0.8')
Salaries <- my_swap2('1,5', '1.5')



Salaries <- my_swap4('e-commerce', 'Ecommerce')
Salaries <- my_swap4('E-commerce', 'Ecommerce')
Salaries <- my_swap4('E-Commerce', 'Ecommerce')
Salaries <- my_swap4('eCommerce', 'Ecommerce')
Salaries <- my_swap4('Financial', 'Finance')
Salaries <- my_swap4('Full-time position in Education, part-time position in at a data startup', 'Education')
Salaries <- my_swap4('Game Company', 'Gaming')
Salaries <- my_swap4('Fintech', 'Finance')
Salaries <- my_swap4('Outsourse', 'Outsource')
Salaries <- my_swap4('Research institute', 'Research')
Salaries <- my_swap4('consumer goods', 'Product')
Salaries <- my_swap4('Outsorce', 'Outsource')
Salaries <- my_swap4('Consulting and Product', 'Consulting / Agency')
Salaries <- my_swap4('IT-Outsourcing', 'Outsource')
Salaries <- my_swap4('Non-tech retail', 'Retail')
Salaries <- my_swap4('Market Research', 'Research')
Salaries <- my_swap4('Old industry', 'Industry')

Salaries <- my_swap5('Boeblingen' , 'Bölingen')
Salaries <- my_swap5('Braunschweig' , 'Brunswick')
Salaries <- my_swap5('Zurich' , 'Zürich')
Salaries <- my_swap5('Warsaw, Poland' , 'Warsaw')
Salaries <- my_swap5('warsaw' , 'Warsaw')
Salaries <- my_swap5('Nuremberg' , 'Nürnberg')
Salaries <- my_swap5('Milan' , 'Milano')
Salaries <- my_swap5('Fr' , 'France')
Salaries <- my_swap5('Konstanz area' , 'Konstanz')
Salaries <- my_swap5('Duesseldorf' , 'Düsseldorf')
Salaries <- my_swap5('Dusseldorf' , 'Düsseldorf')
Salaries <- my_swap5('Dusseldurf' , 'Düsseldorf')

Salaries <- my_swap6('Русский' , 'Russian')
Salaries <- my_swap6('50/50', 'English')
Salaries <- my_swap6('both', 'English')
Salaries <- my_swap6('Russian, English', 'Russian')
Salaries <- my_swap6('English and German', 'English')

Salaries <- my_swap7('C-level executive manager', 'C-Level')
Salaries <- my_swap7('CTO', 'C-Level')
Salaries <- my_swap7('intern', 'Intern')
Salaries <- my_swap7('student', 'Student')
Salaries <- my_swap7('Working Student', 'Student')
Salaries <- my_swap7('Work Center Manager' , 'Manager')
Salaries <- my_swap7('No level', 'Entry level')
Salaries <- my_swap7('no idea, there are no ranges in the firm', 'Entry level')

Salaries <- my_swap8('Dana Analyst' , 'Data Analyst')
Salaries <- my_swap8('Data analyst' , 'Data Analyst')
Salaries <- my_swap8('Engineering manager' , 'Engineering Manager')
Salaries <- my_swap8('Full-Stack Developer' , 'Fullstack Developer')
Salaries <- my_swap8('Fullstack engineer, ну или Software engineer' , 'Software Engineer')
Salaries <- my_swap8('Big Data Engineer' , 'Data Engineer')
Salaries <- my_swap8('data engineer', 'Data Engineer')
Salaries <- my_swap8('Data Engineer' , 'Data Engineer')
Salaries <- my_swap8('Account Managet' , 'Account Manager')
Salaries <- my_swap8('DBA' , 'Database Administrator')
Salaries <- my_swap8('IT Spezialist' , 'IT Specialist')
Salaries <- my_swap8('Project manager' , 'Project Manager')
Salaries <- my_swap8('Rentner' , 'Pensioner')
Salaries <- my_swap8('Researcher/ Consumer Insights Analyst' , 'Researcher')
Salaries <- my_swap8('Security engineer' , 'Security Engineer')
Salaries <- my_swap8('Software Architekt' , 'Software Architect')
Salaries <- my_swap8('Solution Architect' , 'Solutions Architect')
Salaries <- my_swap8('Solutions architect' , 'Solutions Architect')
Salaries <- my_swap8('SRE' , 'Site Reliability Engineer')
Salaries <- my_swap8('support engineer' , 'Support Engineer')
Salaries <- my_swap8('Systemadministrator' , 'System Administrator')
Salaries <- my_swap8('Team lead' , 'Team Lead')
Salaries <- my_swap8('Teamlead' , 'Team Lead')
Salaries <- my_swap8('Tech Lead / Full-Stack' , 'Tech Lead')
Salaries <- my_swap8('Tech Leader' , 'Tech Lead')
Salaries <- my_swap8('Technical Lead' , 'Tech Lead')
Salaries <- my_swap8('Testmanager' , 'Test Manager')
Salaries <- my_swap8('Test manager' , 'Test Manager')
Salaries <- my_swap8('DatabEngineer' , 'Data Engineer')
```

```{r, echo=TRUE}
Salaries$`Total years of experience` <- as.numeric(as.character(Salaries$`Total years of experience`))
```

## Variables
```{r}
names(Salaries)
```

## Cutting Down Responses

```{r, echo=TRUE}
Sex <- c("Male", "Female")
Salaries2 <- Salaries %>% filter(number_responses_per_city > 10 & Base_Salary < 1000000 & Gender %in% Sex & number_people_per_main_tech > 9)
dim(Salaries2)

```

## Exploratory Data Analysis
```{r}
mean_age <-Salaries %>% pull(Age) %>% mean(na.rm = TRUE)
median_age <- Salaries %>% pull(Age) %>% median(na.rm = TRUE)
Age <- Salaries %>% ggplot(aes(x= Age)) + geom_density(fill = "dark blue", alpha = .5) + geom_vline(aes(xintercept = mean_age), size = 1, color = 'red') + geom_vline(aes(xintercept = median_age), size = 1, color = 'orange') + labs(title = 'Age Distribution')
ggplotly(Age)


mean_age2 <-Salaries2 %>% pull(Age) %>% mean(na.rm = TRUE)
median_age2 <- Salaries2 %>% pull(Age) %>% median(na.rm = TRUE)
Age2 <- Salaries2 %>% ggplot(aes(x= Age)) + geom_density(fill = "dark blue", alpha = .5) + geom_vline(aes(xintercept = mean_age2), size = 1, color = 'red') + geom_vline(aes(xintercept = median_age2), size = 1, color = 'orange') + labs(title = 'Age Distribution')
ggplotly(Age2)
```

## Exploratory Data Analysis Pt 2
```{r}
Salaries %>% group_by(Gender) %>% tally() %>%  arrange(desc(n)) %>%  na.omit()

Salaries2 %>% group_by(Gender) %>% tally() %>%  arrange(desc(n)) %>%  na.omit()

```
## Exploratory Data Analysis Pt 3
```{r}
Salaries %>% group_by(City) %>% tally() %>% arrange(desc(n)) %>% head(10)

Salaries2 %>% group_by(City) %>% tally() %>% arrange(desc(n))

```

## Exploratory Data Analysis  Pt 4
```{r}
Salaries %>% group_by(Position) %>% tally() %>% arrange(desc(n)) %>% head(10)

Salaries2 %>% group_by(Position) %>% tally() %>% arrange(desc(n))%>% head(10)

```
## Exploratory Data Analysis Pt 5
```{r}
mean_exp <-Salaries %>% pull(`Total years of experience`) %>% mean(na.rm = TRUE)
median_exp <- Salaries %>% pull(`Total years of experience`) %>% median(na.rm = TRUE)
Exp <- Salaries %>% ggplot(aes(x= `Total years of experience`)) + geom_density(fill = "dark blue", alpha = .5) + geom_vline(aes(xintercept = mean_exp), size = 1, color = 'red') + geom_vline(aes(xintercept = median_exp), size = 1, color = 'orange') + labs(title = 'Experience Distribution', x= 'Total Years of Experience')
ggplotly(Exp)


mean_exp2 <-Salaries2 %>% pull(`Total years of experience`) %>% mean(na.rm = TRUE)
median_exp2 <- Salaries2 %>% pull(`Total years of experience`) %>% median(na.rm = TRUE)
Exp2 <- Salaries2 %>% ggplot(aes(x= `Total years of experience`)) + geom_density(fill = "dark blue", alpha = .5) + geom_vline(aes(xintercept = mean_exp2), size = 1, color = 'red') + geom_vline(aes(xintercept = median_exp2), size = 1, color = 'orange') + labs(title = 'Experience Distribution', x = 'Total Years of Experience')
ggplotly(Exp2)
```

## Exploratory Data Analysis Pt 6
```{r}
Salaries %>% group_by(`Seniority level`) %>% tally() %>% arrange(desc(n)) %>% na.omit() %>% head()

Salaries2 %>% group_by(`Seniority level`) %>% tally() %>% arrange(desc(n)) %>% na.omit() %>% head()

```

## Exploratory Data Analysis Pt 7
```{r}
Salaries %>% group_by(`Main language at work`) %>% tally() %>% arrange(desc(n)) %>% na.omit()%>% head(5)

Salaries2 %>% group_by(`Main language at work`) %>% tally() %>% arrange(desc(n)) %>% na.omit()

```

## Exploratory Data Analysis Pt 8
```{r}
Salaries %>% group_by(`Your main technology / programming language`) %>% tally() %>% arrange(desc(n)) %>% na.omit()%>% head(10)

Salaries2 %>% group_by(`Your main technology / programming language`) %>% tally() %>% arrange(desc(n)) %>% na.omit()%>% head(10)

```

## Exploratory Data Analysis Pt 9
```{r}
mean_salary <-Salaries %>% filter(Base_Salary < 1000000) %>%  pull(Base_Salary) %>% mean(na.rm = TRUE)
median_salary <- Salaries %>% filter(Base_Salary < 1000000) %>% pull(Base_Salary) %>% median(na.rm = TRUE)
Salary<- Salaries %>% filter(Base_Salary < 1000000) %>%  ggplot(aes(x = Base_Salary)) + geom_density(fill = 'blue', alpha = .5) + geom_vline(aes(xintercept = mean_salary), size = .8, color = 'red') + geom_vline(aes(xintercept = median_salary), size = .8, color = 'orange') + labs(title = 'Base Salary Distribution', x = 'Base Salary')
options(scipen = 999)
ggplotly(Salary)

mean_salary2 <-Salaries2 %>% filter(Base_Salary < 1000000) %>%  pull(Base_Salary) %>% mean(na.rm = TRUE)
median_salary2 <- Salaries2 %>% filter(Base_Salary < 1000000) %>% pull(Base_Salary) %>% median(na.rm = TRUE)
Salary2 <- Salaries2 %>% filter(Base_Salary < 1000000) %>%  ggplot(aes(x = Base_Salary)) + geom_density(fill = 'blue', alpha = .5) + geom_vline(aes(xintercept = mean_salary2), size = .8, color = 'red') + geom_vline(aes(xintercept = median_salary2), size = .8, color = 'orange') + labs(title = 'Base Salary Distribution', x = "Base Salary")
options(scipen = 999)
ggplotly(Salary2)
```

## Exploratory Data Analysis Pt 10
```{r}
Salaries2 %>% group_by(`Company size`) %>% tally() %>% arrange(desc(n)) %>% na.omit()


Salaries2 %>% group_by(`Company type`) %>% tally() %>% arrange(desc(n)) %>% na.omit()%>% head(5)
```


## Experience Vs Salary
### City, Gender, And Main Tech Used

```{r}
ExpGenderVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = Gender)) + geom_point(alpha = .5) + scale_x_log10() + labs(title = 'Experience vs Salary Based On Gender', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpGenderVSalary)

ExpCityVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = City)) + geom_point(alpha = .5) + scale_x_log10()+ labs(title = 'Experience vs Salary Based On Location', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpCityVSalary)


ExpProgramVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = `Your main technology / programming language`)) + geom_point(alpha = .5) + scale_x_log10() + labs(title = 'Experience vs Salary Based On Main Programming Language Used', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpProgramVSalary)

```

## Experience Vs Salary Pt. 2
### Position and Seniority Level
```{r}
ExpPositionVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = Position)) + geom_point(alpha = .5) + scale_x_log10()+ labs(title = 'Experience vs Salary Based On Position', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpPositionVSalary)



ExpSeniorityVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = `Seniority level`)) + geom_point(alpha = .5) + scale_x_log10() + labs(title = 'Experience vs Salary Based On Seniority Level', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpSeniorityVSalary)
```

## Experience Vs Salary Pt. 3
### Company Size and Type
```{r}
ExpCompSizeVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = `Company size`)) + geom_point(alpha = .5) + scale_x_log10() + labs(title = 'Experience vs Salary Based On Company Size', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpCompSizeVSalary)


ExpCompTypeVSalary <- Salaries2 %>% ggplot(aes(x = `Total years of experience`, y = Base_Salary, fill = `Company type`)) + geom_point(alpha = .5) + scale_x_log10() + labs(title = 'Experience vs Salary Based On Company Type', x = 'Total Years of Experience', y = 'Base Salary')
ggplotly(ExpCompTypeVSalary)
```

## Summary
- Age: 23-42
- Gender: Male
- City: Berlin or Munich
- Programming Language: C, Java, Python
- Years of Experience: 4-12 
- Company Type: Product or startup
- Company Size: Any
- Seniority: Lead, Head, Manager